Demand Forecasting of Individual Probability Density Functions with Machine Learning

### 2021-06-21 LaTex/paper.tex
few additional sentences for SNORF resubmit

% Michael am Ende als "PI"
\author[1]{Felix Wick}
\author[3]{Ulrich Kerzel}
\author[1]{Martin Hahn}
\author[1]{Moritz Wolf}
\author[2]{Trapti Singhal}
\author[1]{Daniel Stemmer}
\author[1]{Jakob Ernst}
\author[1]{Michael Feindt}
\affil[1]{\small Blue Yonder GmbH (Ohiostra{\ss}e 8, 76149 Karlsruhe, Germany)}
\affil[2]{\small Blue Yonder India Private Limited (Bengaluru, India)}
\affil[3]{\small IUBH Internationale Hochschule (Erfurt, Germany)}

@@

The contribution of this paper is two-fold:

@@

The general methods developed in this paper can be applied to any setting that requires the prediction and evaluation of probability distributions from observational data, not just demand forecasting. However, to make the impact and benefits more tangible in a practical setting, we limit the discussion to demand forecasting in retail.

@@

As forecasting relies upon statistical dependencies, no matter if spurious or from true causal effects, this does not seem to be a problem for the predictive power at first glance. However, it can have severe impacts on the explainability and generalizability of the model, because the autocorrelation, being a composed effect of many causes, is less stable over time than the actual causal effects. A concrete weakness of the reliance on autocorrelation can be seen when looking at effects at isolated time steps. For example, if the target variable has a sharp peak that is induced by a sudden change of an exogenous variable with a causal influence on the target, the autocorrelation, lagged by its nature, would not help to predict the peak at the very day it occurs, but would tend to ``trick'' the model in predicting a delayed peak, which in turn reduces the accuracy of the prediction at other time steps after the actual peak as well.

>>>>

% Michael am Ende als "PI"
\author[1]{Felix Wick}
\author[3]{Ulrich Kerzel}
\author[1]{Martin Hahn}
\author[1]{Moritz Wolf}
\author[2]{Trapti Singhal}
\author[1]{Daniel Stemmer}
\author[1]{Jakob Ernst}
\author[1]{Michael Feindt}
\affil[1]{\small Blue Yonder GmbH (Ohiostra{\ss}e 8, 76149 Karlsruhe, Germany)}
\affil[2]{\small Blue Yonder India Private Limited (Bengaluru, India)}
\affil[3]{\small IU Internationale Hochschule (Erfurt, Germany)}

@@

This work brings together elements from three different fields: operations research, machine learning, and causal inference. The combination of these allows to build state-of-the-art demand forecasting models that are fully explainable and incorporate the causal structure of demand. The contribution of this paper is two-fold:

@@

The general methods developed in this paper can be applied to any setting that requires the prediction and evaluation of probability distributions from observational data, not just demand forecasting. However, to make the impact and benefits more tangible in a practical setting, as well as describe a general methodology how to build such systems from a practitioner's perspective, we limit the discussion to demand forecasting in retail.

@@

As traditional statistical forecasting or machine learning methods generally rely upon statistical dependencies, no matter if spurious or from true causal effects, this does not seem to be a problem for the predictive power at first glance. However, it can have severe impacts on the explainability and generalizability of the model, because the autocorrelation, being a composed effect of many causes, is less stable over time than the actual causal effects. A concrete weakness of the reliance on autocorrelation can be seen when looking at effects at isolated time steps. For example, if the target variable has a sharp peak that is induced by a sudden change of an exogenous variable with a causal influence on the target, the autocorrelation, lagged by its nature, would not help to predict the peak at the very day it occurs, but would tend to ``trick'' the model in predicting a delayed peak, which in turn reduces the accuracy of the prediction at other time steps after the actual peak as well.
